README

### 2019-04-09 Code/dallin_annotations/02_create_clustering_function.Rmd
More documentation and troubleshooting.

### Code I don't understand
```{r}
# I imagine that this somehow takes a look at the nearest neigbors of a single word, or a tweet vector?
 nn_filter <- function(model, token, filter_str, n = 1000) {
  out <- get_nn(model, token, n)
  if(!is.na(filter_str)) {
    tibble(word = names(out), value = out) %>% 
      filter(!grepl(paste0(".*", filter_str, ".*"), word, ignore.case = T))
  } else {
    tibble(word = names(out), value = out)
  }
}

>>>>

### Code I don't understand, other than that it is a list of many functions created. 
The functions are: nn_filter, model_eval, GetDotObjectNames, model_eval_plot, model_eval_plot_wrap, and wss_func.
```{r}
# I imagine that this somehow takes a look at the nearest neigbors of a single word, or a tweet vector?
 nn_filter <- function(model, token, filter_str, n = 1000) {
  out <- get_nn(model, token, n)
  if(!is.na(filter_str)) {
    tibble(word = names(out), value = out) %>% 
      filter(!grepl(paste0(".*", filter_str, ".*"), word, ignore.case = T))
  } else {
    tibble(word = names(out), value = out)
  }
}

### 2019-04-09 Code/dallin_annotations/08_classifier_construction.Rmd
More documentation and troubleshooting.

# Libraries
```{r}
library(tidyverse)
library(fastrtext)
library(magrittr) # for assignment operator %<>% 
library(plotly)
require(randomForest)
library(Matrix)
source("R/clus_func.R")
source("R/logit_classifier_func.R")

@@

# file to read tweets from. Should be a txt file with one tweet per line
file_txt <- "../../Temporary/tweet_sample_2M_noRT.txt"

@@

# train the unsupervised fasttext model
#fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))

@@

# read in labeled traing data
train <- read_csv("data/Marketing Research Labeled Tweets All 12-05-18.csv")

@@

train %<>% 
  mutate(tweetFeatures = map(tweet_text, TweetFeatures))

# create a list column that contains all of features output by the fasttext model
train %<>% 
  mutate(avg_vec_50 = map(tweet_text, VectorizeTweet, model = fasttext_model))

>>>>

This file is extremely important because it is where Adriel built the "frankenstein" model.

Here are two important models built by this script:
model50-tweet_sample_2M_noRT.dat
xgb.modelPC4-xgb_version.dat

# Libraries
```{r}
library(tidyverse)
library(fastrtext)
library(magrittr) # for assignment operator %<>% 
library(plotly)
require(randomForest)
library(Matrix)
source("../complaint-prediction/R/clus_func.R")
# source("../complaint-prediction/R/logit_classifier_func.R") This file does not exist

# source("02_create_clusteringifunction.Rmd") New files not yet

@@

# file to read tweets from. Should be a txt file with one tweet per line
# file_txt <- "../../Temporary/tweet_sample_2M_noRT.txt"
file_txt <- "../../Temporary/tweet_sample_1hM_noRT.txt"

@@

# train the unsupervised fasttext model
# fastrtext::execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))

@@

# read in labeled traing data
train <- read_csv("../../Temporary/train_test_data/Marketing Research Labeled Tweets_ - tweet_sample_5k_Ky-Ch-Ad.csv")

@@

train <- train %>% 
  mutate(tweetFeatures = map(tweet_text, TweetFeatures))

# create a list column that contains all of features output by the fasttext model
train <- train %>%
  mutate(avg_vec_50 = map(tweet_text, VectorizeTweet, model = fasttext_model))

### 2019-04-09 Code/dallin_annotations/09_fasttext_clust_EDA.Rmd
More documentation and troubleshooting.

```{r}
library(googlesheets)
library(plotly)
library(broom)
library(caret)
library(cluster)
library(qtlcharts)
library(RPostgreSQL)
library(dbplyr)
source("Code/complaint-prediction/R/clus_func.R")

@@

sample_tweets %>%
  .$tweet_text %>% 
  write_lines("data/tweet_sample_1mil.txt")

@@

sample_tweets %>%
  .$tweet_text %>%
  write_lines("data/tweet_sample_1hM_noRT.txt")
rm(sample_tweets) # After writing the .txt files, we are removing them from the environment with the rm() function

@@

sample_tweets %>%
  .$tweet_text %>%
  write_lines("data/tweet_sample_2M_noRT.txt")
rm(sample_tweets)

@@

file_txt <- "data/tweet_sample_1hM_noRT.txt"

file_model200 <- "data/models/model200.dat"
file_model150 <- "data/models/model150.dat"
file_model100 <- "data/models/model100.dat"
file_model50  <- "data/models/model50.dat"
file_model25  <- "data/models/mode25.dat"

 execute(commands = c("cbow", "-input", file_txt, "-output", file_model200, "-verbose", 1, "-dim", 200))
model200 <- load_model(file_model200)

 execute(commands = c("cbow", "-input", file_txt, "-output", file_model150, "-verbose", 1, "-dim", 150))
model150 <- load_model(file_model150)

 execute(commands = c("cbow", "-input", file_txt, "-output", file_model100, "-verbose", 1, "-dim", 100))
model100 <- load_model(file_model100)

 execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 1, "-dim", 50))
model50 <- load_model(file_model50)

 execute(commands = c("cbow", "-input", file_txt, "-output", file_model25, "-verbose", 1, "-dim", 25))
model25 <- load_model(file_model25)

@@

sample_tweets <- 
  read_lines("data/tweet_sample_1hM_noRT.txt") %>% 
  tibble(tweet_text)

>>>>

```{r}
library(googlesheets)
library(plotly)
library(broom)
library(caret)
library(cluster)
library(qtlcharts)
library(RPostgreSQL)
library(dbplyr)
source("../complaint-prediction/R/clus_func.R")

@@

getwd()

sample_tweets %>%
  .$tweet_text %>% 
  write_lines("../../Temporary/tweet_sample_1mil.txt")

@@

sample_tweets %>%
  .$tweet_text %>%
  write_lines("../../Temporary/tweet_sample_1hM_noRT.txt")
rm(sample_tweets) # After writing the .txt files, we are removing them from the environment with the rm() function

@@

sample_tweets %>%
  .$tweet_text %>%
  write_lines("../../Temporary/tweet_sample_2M_noRT.txt")
rm(sample_tweets)

@@

file_txt <- "../../Temporary/tweet_sample_1hM_noRT.txt"

file_model200 <- "../../Temporary/model200.dat"
file_model150 <- "../../Temporary/model150.dat"
file_model100 <- "../../Temporary/model100.dat"
file_model50  <- "../../Temporary/model50.dat"
file_model25  <- "../../Temporary/mode25.dat"

 # execute(commands = c("cbow", "-input", file_txt, "-output", file_model200, "-verbose", 1, "-dim", 200))
model200 <- load_model(file_model200)

 # execute(commands = c("cbow", "-input", file_txt, "-output", file_model150, "-verbose", 4, "-dim", 150))
model150 <- load_model(file_model150)

 # execute(commands = c("cbow", "-input", file_txt, "-output", file_model100, "-verbose", 4, "-dim", 100))
model100 <- load_model(file_model100)

 # execute(commands = c("cbow", "-input", file_txt, "-output", file_model50, "-verbose", 4, "-dim", 50))
model50 <- load_model(file_model50)

 # execute(commands = c("cbow", "-input", file_txt, "-output", file_model25, "-verbose", 4, "-dim", 25))
model25 <- load_model(file_model25)

@@

sample_tweets <- 
  read_lines("../../Temporary/tweet_sample_1hM_noRT.txt") %>% 
  tibble(tweet_text = .)

### 2019-04-09 Code/dallin_annotations/README.Rmd
More documentation and troubleshooting.

### 08_classifier_construction.Rmd

@@

### 11_predict_func.Rmd

### 12_tweet_complaint_predictor.Rmd

@@

>>>>

### 08_classifier_construction.Rmd
This document contains the code that builds models referenced in other files, namely the model50-tweet_sample_2M_noRT.dat and xgb.modelPC4-xgb_version.dat

@@

### 11_predict_func.Rmd
This file contains a lot of useful functions for our model, such as the VectorizeTweet function.

### 12_tweet_complaint_predictor.Rmd
tweet_complaint_predictor.Rmd builds a function named newTweetComplaintPredictor, which is referenced in serveral other scripts.

@@

Note: I can't seem to find the logit_classifier_func.R file anywhere. It's referenced in classifier_construction.R
